First Detection of the Environmental Dependence of the Structures of Massive Galaxies

### 2016-12-06 draft/ms_v1.tex
Update 12/06

\def\minn{{$M_{\star,10\mathrm{kpc}}$}}
\def\mtot{{$M_{\star,100\mathrm{kpc}}$}}
\def\mout{{$M_{\star,150\mathrm{kpc}}$}}
\def\mgama{{$M_{\star,\mathrm{GAMA}}$}}
\def\mcmodel{{$M_{\star,\mathrm{cModel}}$}}

\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmgama{{$\log (M_{\star,mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log (M_{\star,mathrm{cModel}}/M_{\odot})$}}

@@

    \begin{itemize}
        \item \update{\mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
            core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ 
            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) in massive galaxies.  
            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
            phase.  Although it is an empirical choice, the detailed comparison of 
            \mden{} profiles later suggests it indeed helps reveal interesting 
            environmental dependence.  
            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5.  
            We can reliably measure \minn{} without being bothered by smearing effect
            of seeing.}
        \item \update{\mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
            Limited by the accuracy of background subtraction, the \mden{} profile 
            of outer region can not be reliably recovered for massive galaxies across 
            our redshift range. 
            Although not perfect, \mtot{} is still a much better tracer of total 
            \mstar{} than the model-dependent ones using shallower images.}
    \end{itemize}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
      	Left: Median \mden{} profiles of galaxies in different \mtot{} bins:
      	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
      	[11.8, 12.0] (long-dashed line). 
      	Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random subset 
      	of individual profiles in the background.
      	The shaded region highlights the region that could be affected by PSF.
        Two vertical lines label the radius of 10 kpc (thin, dotted line) and
        100 kpc (thick, dash line). ~~~ 
        Right: comparison between the average \mden{} profiles with the ones from 
        previous observations and simulations, including: 
        1) average profile of massive elliptical galaxies at $z\sim 0$ from 
        \citet[][Cyan, solid]{Huang2013a}; 
        2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
        \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
        3) average radial stellar distribuitions in massive halos using simulation and 
        particle tagging method (\citealt{Cooper13}; Purple, short-dashed).}
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \update{
      Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
      and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
      of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.
      \textbf{Left} shows the results for the \mtot{}-matched samples.
      For details of the matching process, please see Appendix.\ref{app:match}.  
      On its upper panel, we show the \mden{} profile of each galaxy using very light 
      color in the background.  
      We highlight the median profile and its corresponding uncertainties using thick 
      solid line with darker color and shaded region. 
      Other formats are the same with Fig.\ref{fig:avg_prof}.
      Meanwhile, we highlight the difference between the median profiles and its 
      uncertainty on the bottom panel (brown solid line and shaded region).
      To test the significance of the differential profile, we perform statistical tests 
      by comparing the median profiles of two random groups that are drawn from the 
      mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
      Repeating this process many times, the median of these random differential 
      profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
      (light-grey shaded region) uncertainties are shown on the bottom panel as well. 
      A darker vertical dash-line highlights the 100 kpc radius.~~
      \textbf{Right} shows the results for the \minn{}-matched samples. 
      The format is exactly the same with the left one, except that the darker vertical 
      dash-line now highlights the 10 kpc radius.}
      \label{fig:prof_m100_A}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    \song{Due to the change of figure, this section has been updated slightly}

@@

    \update{
    Before dive into more details, we first show the average \mden{} of massive galaxies 
    at $0.3 < z < 0.5$ in three \mtot{} bins after mixing the \rbcg{} and \nbcg{} 
    samples together\footnote{Knowing that the two samples have different levels of 
    completeness, here we simply mean to show the general properties of massive galaxies.
    In the first two \mtot{} bins, the \nbcg{} galaxies dominate the number; while in
    the highest \mtot{} bin, the two samples have roughly the same size.}.   
    For \mden{} profiles in each \mtot{} bin, we derive the median profile along with its 
    uncertainty using bootstrap resampling method (5000 times). 
    In the left panel of Fig.\ref{fig:avg_prof}, we can see that the higher \mtot{} 
    shifts the median \mden{} profile up a little bit in the inner region, but makes 
    the outskirt significantly more prominent. 
    Most of these very massive galaxies ($\ge 10^{11.4} M_{\odot}$) should be 
    slow-rotating (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner 
    isophotal shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile 
    around the center (e.g.\ \citealt{Lauer07}).
    But their structures in the outskirt clearly does \textbf{NOT} response to the 
    increase of ``total'' stellar mass in a self-similar way.}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
      \caption{Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
      	(grey-black) galaxies in lower (left; [11.5,11.70]) and higher 
        (right; [11.7, 11.9]) \mtot{} bins. 
        Other formats are in consistent with the right figure of 
        Fig.\ref{fig:prof_m100_A}.
        The difference in median profiles is more significant in higher \mtot{} bin.
        \song{Figure has been updated, but need to update the caption.}
        }
      \label{fig:prof_m100_C}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_m10C}
      \caption{\alexie{There is a lot of redundancy in the Figures. I'm going to suggest to bring all the main figures together in a 4 panel figure?}. Comparisons of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
          (grey-black) samples that are matched using \minn{} instead of \mtot{}. 
          We perform the match at $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.6$.
          \textbf{Left figure} shows the matching results in the same format with 
          the left figure of Fig.\ref{fig:prof_m100_A}.  
          The only difference is \mtot{} is replaced by \minn{}. ~~~
          \textbf{Middle figure} summarizes the profile comparisons in the same format 
          with the right figure of Fig.\ref{fig:prof_m100_A}.~~~
          \textbf{Right figure} is very similar to the middle one, except we show the 
          profiles that are normalized using the \minn{} value to highlight the 
          scatters of \mden{} at different radius. 
          \alexie{the tow figures actually look pretty similar. I think most people will not notice the difference. Pick one and go with that. I guess I have a preference for the unnormalized one. Your mathced sampeles take care of the reason we made the normalized versions. (mean mass was different between samples.)}
          \song{Ok, will only use the unnormalized ones later; The point of normalized one is to 
          reduce the effect of the \mstar{} width of the mass bin; it is useful when I 
          discuss the dispersion of \mden{} at outer radius; I could simply emphasis that 
          in the text, or put some figures in the Appendix....how many appendix is too
          many}}
      \label{fig:prof_m10_A}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    \song{Still need a little bit text here}

    We show the results of the comparison in Fig.\ref{fig:prof_m100_A}. 
    The left panel highlights the properties of the matched \rbcg{} and \nbcg{} 
    samples.
    Given the typical uncertainty of stellar mass, the two samples are well 
    matched in \mtot{}; and their redshift distributions are broadly 
    consistent with each other.  
    We also check their distributions of $k$-corrected colors ($g-r$), and confirm 
    that they have very similar average color distributions as well.  
    For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
    matched sample.
    On the right side, we plot the individual stellar mass density (\mden{}) profile 
    of \rbcg{} and \nbcg{} galaxies along with the median profiles of both samples. 
    The uncertainties of the median profiles are derived using 5000 times of 
    bootstrap resampling.
    As one can see, we can comfortably trace the \mstar{} distribution of these massive 
    galaxies out to 100 kpc at individual level, which gives us huge advantage in 
    studying the statistical properties of their outer envelopes. 
    Mass profile out to such large radius was only available for large sample of 
    massive galaxies through image stacking method (\addref) which suffers from certain
    systematic issues. 
    Although the \mden{} profiles of many galaxies extend well beyond the 100 kpc radius, 
    we notice that some profiles show sign of unphysical truncation that is caused 
    by inaccurate background subtraction.  
    Therefore, we will not include profiles outside 100 kpc in the comparison, even 
    though the median profiles within 200 kpc still behave normally.

    Once we match the distributions of \mtot{}, the \mden{} profiles of massive 
    galaxies in the \rbcg{} and \nbcg{} samples \textbf{greatly overlap with each 
    other over the entire radius range}. 
    At fixed ``total'' stellar mass, massive central galaxies of more massive 
    halos do not form a unique population comparing to the ones from less massive 
    halos in term of the stellar mass distributions.

    At the same time, thanks to the high quality individual profile from HSC image, 
    we can also spot interesting differences in the median profiles of the \mtot{} 
    matched \rbcg{} and \nbcg{} samples.  
    In details, it seems that central galaxy in more massive halos tends to have 
    a slightly flattened inner density profile and possess more significant outer 
    envelope.   
    To highlight such subtle structural features, we show the difference between 
    the two median profiles and its uncertainty in the bottom panel. 
    Given the noticeable uncertainties of \mtot{} and $\lambda$, and the current small 
    sample sizes, we also perform statistical test to confirm the robustness of the
    result: we mix the $N_{\mathrm{r}}$ \rbcg{} galaxies and the $N_{\mathrm{n}}$ \nbcg{}
    ones together, then randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, 
    compute the difference between the median profile of this sample and the \nbcg{} 
    sample, and repeat this process 2000 times.  
    Comparing with the statistical distributions of the differential profiles from 
    this test (grey shaded region), we can now conclude that the structural 
    differences between \rbcg{} and \nbcg{} samples are much more significant than 
    any statistical fluctuation given the current samples.  
    And, apparently, the ``transition radius'' where the median profiles of \rbcg{} 
    and \nbcg{} sample have the same \mden{} is $\sim 15$-20 kpc, which is quite 
    close to the expected $R_{\mathrm{e}}$ of ETGs at this stellar mass.

    To further test the robustness of this interesting result, we repeat above 
    procedures to samples with slightly different definition.  
    The results are shown in Fig.\ref{fig:prof_m100_B}: 
    (a). At higher redshift, the profile is more affected by the seeing at inner 
    region, and by the imaging depth in the outskirt.  
    Therefore, in the left panel, we compare the \rbcg{} and \nbcg{} samples at 
    $0.3 \leq z < 0.4$, and the results are very similar.
    (b). We also make the comparison using a \rbcg{} sample with lower average 
    halo mass ($\lambda \geq 20$), the results are still stable (middle panel). 
    We also check whether the structural differences are driven by small fraction 
    of \rbcg{} galaxies in very massive clusters.  
    After removing the \rbcg{} galaxies in clusters with $\lambda \geq 40$, the 
    differences are as significant as above.  
    (c). As noted before, the \mtot{} is just a proxy of the total stellar mass. 
    Given the differences we find, at fixed \mtot{}, \rbcg{} galaxy tends to have 
    more prominent outer envelope outside 100 kpc than the \nbcg{} one. 
    Hence their real ``total'' stellar mass could also be slightly larger, and 
    result in bias in the comparison.  
    In the right panel, we make the comparison using the maximum stellar mass from 
    the integration of the \mden{} profile instead of the \mtot{}.
    In this case, the differences between the median profiles become slightly 
    less significant as expected.  
    But the systematic trends, especially the differences in the low mass density 
    outskirt are still very stable.  
    All these tests confirm that we robustly detect subtle, but systematic 
    structural dependence on halo mass of massive galaxies.   
    The fact that it requires such careful comparison to reliably reveal any 
    potential halo mass dependence already suggests that the role environment
    played in shaping these massive galaxies is not crucially important.  
    At the same time, the systematic differences we find, especially the more 
    extended stellar envelope of massive central galaxy in more massive halos, 
    seem to be consistent with the expectation of richer (minor) merging history
    in denser environment. 
    We will discuss these more in Section \ref{sec:discussion}.

    We also explore the possible \mtot{} dependence of such difference.  
    Limited by the small sample we have, we can only afford to separate the 
    samples into two \mtot{} bins 
    ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
     $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$).  
    After performing the same procedures of sample matching and comparison, 
    we show the results in Fig.\ref{fig:prof_m100_C}.  
    Although the smaller sample leads to larger statistical uncertainties, 
    it is still interesting to see that the structural differences seem to 
    be more significant in the higher \mtot{} bin.  
    For the lower \mtot{} bin, the difference in the inner region becomes quite 
    uncertain, while there is still evidence that suggest difference in the 
    outskirt.  
    This result also has interesting implications in studying the assembly 
    of massive galaxies, and is worth further investigation with larger sample
    in the future.

@@

\subsubsection{Matched Samples Using \minn{}}
    \label{sssec:sbp_minn}

    \song{Got it! will update later}
    \alexie{This paragraph goes in the discussions section. The results section should be "We now do this to the data and here is the Figure"} As suggested by the popular two-phase formation scenario of massive galaxies, 
    the inner 5-10 kpc of these galaxies (within 0.5-1$xR_{\mathrm{e}}$) is 
    dominated by stars formed in intensive dissipative processes at high redshift, 
    and is less affected by the succeeding merging events.  
    This picture is broadly supported by the redshift evolution of \mden{} profile
    of massive galaxies (\addref), structure decomposition of nearby massive galaxies 
    (\addref), and their radial distributions of stellar population (\addref).      
    Certainly, major merger can induce violent relaxation process that modifies the 
    stellar mass distribution even in the central region, and must happen to 
    these massive galaxies in last 6-8 Gyrs, it may not invalidate the above assumption.
    For galaxy this massive, the last major merger event is highly likely to be
    non-dissipative, and the redistribution of stars is basically according to their 
    binding energy in the host halo.  
    The inner region of the final merger remnant is still mostly composed 
    of the ``in-situ'' stars from the two progenitors.

>>>>

\def\minn{{$M_{\star,10\mathrm{kpc}}$}}
\def\meff{{$M_{\star,15\mathrm{kpc}}$}} 
\def\mtot{{$M_{\star,100\mathrm{kpc}}$}}
\def\mout{{$M_{\star,150\mathrm{kpc}}$}}
\def\mmax{{$M_{\star,\mathrm{Max}}$}}
\def\mgama{{$M_{\star,\mathrm{GAMA}}$}}
\def\mcmodel{{$M_{\star,\mathrm{cModel}}$}}

\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
\def\logmgama{{$\log (M_{\star,mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log (M_{\star,mathrm{cModel}}/M_{\odot})$}}

@@

    \begin{itemize}
        \item \update{\mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
            core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ 
            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) in massive galaxies.  
            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
            phase.  Although it is an empirical choice, the detailed comparison of 
            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
            helps reveal interesting environmental dependence.  
            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5.  
            We can reliably measure \minn{} without being bothered by smearing effect
            of seeing.}
        \item \update{\mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
            Limited by the accuracy of background subtraction, the \mden{} profile 
            of outer region can not be reliably recovered for massive galaxies across 
            our redshift range. 
            Although not perfect, \mtot{} is still a much better tracer of total 
            \mstar{} than the model-dependent ones using shallower images.}
    \end{itemize}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
      	\textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
      	[11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
      	[11.8, 12.0] (long-dashed line). 
      	Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random subset 
      	of individual profiles in the background.
      	The shaded region highlights the region that could be affected by PSF.
        Two vertical lines label the radius of 10 kpc (thin, dotted line) and
        100 kpc (thick, dash line). ~~~ 
        \textbf{Right}: comparison between the average \mden{} profiles with the ones 
        from previous observations and simulations, including: 
        1) average profile of massive elliptical galaxies at $z\sim 0$ from 
        \citet[][Cyan, solid]{Huang2013a}; 
        2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
        \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
        3) average radial stellar distribuitions in massive halos using simulation and 
        particle tagging method (\citealt{Cooper13}; Purple, short-dashed).}
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          \update{
          Comparison of the \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) 
          and \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples 
          of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
          \textbf{Left} shows the results for the \mtot{}-matched samples.
          For details of the matching process, please see Appendix.\ref{app:match}.  
          On its upper panel, we show the \mden{} profile of each galaxy using very light 
          color in the background.  
          We highlight the median profile and its corresponding uncertainties using thick 
          solid line with darker color and shaded region. 
          Other formats are the same with Fig.\ref{fig:avg_prof}.
          Meanwhile, we highlight the difference between the median profiles and its 
          uncertainty on the bottom panel (brown solid line and shaded region).
          To test the significance of the differential profile, we perform statistical tests 
          by comparing the median profiles of two random groups that are drawn from the 
          mixed sample, and have the same sizes with the matched \rbcg{} and \nbcg{} ones.
          Repeating this process many times, the median of these random differential 
          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 3-$\sigma$
          (light-grey shaded region) uncertainties are shown on the bottom panel as well. 
          A darker vertical dash-line highlights the 100 kpc radius.~~
          \textbf{Right} shows the results for the \minn{}-matched samples. 
          The format is exactly the same with the left one, except that the darker vertical 
          dash-line now highlights the 10 kpc radius.}
      }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

@@

    \update{
    Before dive into more details, we first show the average \mden{} of massive galaxies 
    at $0.3 < z < 0.5$ in three \mtot{} bins after mixing the \rbcg{} and \nbcg{} 
    samples together\footnote{Knowing that the two samples have different levels of 
    completeness, here we simply mean to show the general properties of massive galaxies.
    In the first two \mtot{} bins, the \nbcg{} galaxies dominate the number; while in
    the highest \mtot{} bin, the two samples have roughly the same size.}.   
    For \mden{} profiles in each \mtot{} bin, we derive the median profile along with its 
    uncertainty using bootstrap resampling method (5000 times). 
    As one can see in the left panel of Fig.\ref{fig:avg_prof}, we can comfortably trace 
    the \mstar{} distribution of these massive galaxies out to 100 kpc 
    \textbf{individually}, which gives us huge advantage in studying the statistical 
    properties of their outer envelopes. 
    We can see that the higher \mtot{} shifts the median \mden{} profile up a little bit 
    in the inner region, but makes the outskirt significantly more prominent. 
    Most of these very massive galaxies ($\ge 10^{11.4} M_{\odot}$) should be 
    slow-rotating (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner 
    isophotal shape (e.g.\ \citealt{Kormendy2009}), and slightly flattened \mden{} profile 
    around the center (e.g.\ \citealt{Lauer07}).
    But their structures in the outskirt clearly does \textbf{NOT} response to the 
    increase of ``total'' stellar mass in a self-similar way.}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
      \caption{Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
          and higher (right; [11.7, 11.9]) \mtot{} bins. 
          Other formats are in consistent with the right figure of Fig.\ref{fig:prof_1}.
          The difference in median profiles is more significant in higher \mtot{} bin.}
      \label{fig:prof_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

@@

    \update{
    We show the results of the comparison in Fig.\ref{fig:prof_1} after 
    carefully matching the \rbcg{} sample with smaller size to the \nbcg{} samples 
    within $0.3 < z < 0.5$ and $11.6 < $\logmtot{}$<11.9$ vial searching for the $N$ 
    nearest neighbours on the $M_{\star}$-redshift plane using the KDTree algorithm. 
    The details of the procedure and the evaluation of the matching quality can be 
    found in Appendix.\ref{app:match}. 
    In summary, given the typical uncertainty of stellar mass, the two samples are well 
    matched in \mtot{}; and their redshift distributions are broadly consistent with 
    each other, hence we can perform meaning comparison of their average structures at 
    ``fixed stellar mass'' (median \logmtot{}$\sim 11.74$).    
    We also check their distributions of $k$-corrected colors ($g-r$), and confirm 
    that they have similar color distributions as well.}

    For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
    matched sample.
    \update{
    On the left side of Fig.\ref{fig:prof_1}, we plot the individual \mden{} profile 
    of \rbcg{} and \nbcg{} galaxies along with the median profiles of both samples.
    The uncertainties of the median profiles are derived using 5000 times of 
    bootstrap resampling.
    The \mden{} profile out to such large radius was only available for large sample of 
    massive galaxies through image stacking method (e.g. \citep{Tal2011, DSouza2015}) 
    which suffers from certain systematic issues.}
    Although the \mden{} profiles of many galaxies extend well beyond the 100 kpc radius, 
    we notice that some profiles show sign of unphysical truncation that is caused 
    by inaccurate background subtraction.  
    Therefore, we will not include profiles outside 100 kpc in the comparison, even 
    though the median profiles within 200 kpc still behave normally.

    Once we match the distributions of \mtot{}, the \mden{} profiles of massive 
    galaxies in the \rbcg{} and \nbcg{} samples \textbf{greatly overlap with each 
    other over the entire radius range}. 
    At fixed ``total'' stellar mass, massive central galaxies in more massive 
    halos do not form a unique population comparing to the ones from less massive 
    halos in term of their radial \mstar{} distributions. 
    \update{
    This partially explains why the previous works have trouble finding any clear 
    environmental dependence of structure.}

    At the same time, thanks to the high-quality individual profile from HSC image, 
    we can also spot interesting differences in the median profiles of the 
    \mtot{}-matched \rbcg{} and \nbcg{} samples.  
    In details, it seems that the central galaxies in more massive halos tend to 
    have slightly flattened inner \mden{} profiles while also possess more significant 
    outer stellar envelope.   
    To highlight such subtle structural features, we show the difference between 
    the two median profiles and its uncertainty in the bottom panel. 
    Given the noticeable uncertainties of \mtot{} and $\lambda$, along with the 
    small size of the current \rbcg{} sample, we perform statistical test to confirm 
    the robustness of the result: we mix the $N_{\mathrm{r}}$ \rbcg{} galaxies and 
    the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then randomly draw 
    $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference between the 
    median profile of this sample and the \nbcg{} sample. 
    \update{
    After repeating this process 2000 times, we can evaluate the possibility that 
    the systematic differences in median \mden{} profiles can be reproduced by random 
    selection of massive galaxies.
    Comparing with the statistical distributions of the differential profiles from 
    this test (grey shaded region), we can now conclude that the structural 
    differences between \rbcg{} and \nbcg{} samples are significant.}
    Apparently, the ``transition radius'' where the median profiles of \rbcg{} 
    and \nbcg{} sample have the same \mden{} is $\sim 15$-20 kpc, which is quite 
    close to the expected $R_{\mathrm{e}}$ of ETGs at this \mtot{} (please see 
    next section for details).

    To further test the robustness of this interesting result, we apply the above 
    procedures to \mtot{}-matched samples with slightly different definitions.  
    The results are shown in Fig.\ref{fig:prof_3} in Appendix.\ref{app:robust}: 
    (a). At higher redshift, the profile is affected more by the seeing at inner 
    region, and by the imaging depth in the outskirt.  
    Therefore, we compare the matched \rbcg{} and \nbcg{} samples within 
    $0.3 \leq z < 0.4$, and the results are very similar.
    (b). We also make the comparison using a \rbcg{} sample with lower average 
    halo mass ($\lambda \geq 20$), the results are still stable (middle panel). 
    We also check whether the structural differences are driven by small fraction 
    of \rbcg{} galaxies in very massive clusters.  
    After removing the \rbcg{} galaxies in clusters with $\lambda \geq 40$, the 
    differences are as significant as above.  
    (c). As noted before, the \mtot{} is just a proxy of the total stellar mass. 
    Given the differences we find, at fixed \mtot{}, \rbcg{} galaxy tends to have 
    slightly more prominent outer envelope outside 100 kpc than the \nbcg{} one. 
    Hence their real ``total'' stellar mass could also be slightly larger, and 
    bias the comparison.  
    Therefore, we make a similar comparison using the maximum \mstar{} from 
    the integration of the \mden{} profile instead of the \mtot{}.
    \update{
    In this case, the differences between the median profiles become slightly 
    less significant as expected (a fraction of \rbcg{} galaxies become more 
    massive, and is not included in the \logmtot{}$< 11.9$ mass bin). 
    But the systematic trends, especially the differences in the low mass density 
    outskirt are still very robust. 
    We will further discuss this in Section \ref{sec:discussion}. 
    Considering the uncertainty of \mden{} profiles outside 100 kpc, the 
    feasibility of applying the average \m2l{} to stars in the extreme outskirt, 
    and the contribution of the diffuse stellar components that trace the halo, 
    we think that our results are stable.}

    \textbf{All these tests confirm that we robustly detect subtle, but systematic 
    \mhalo{}-dependence (environmental dependence) of structure in massive, 
    central galaxies.}
    \update{
    Interestingly, the fact the it takes much better data and really cautious 
    comparison to detect such systematic difference seems to suggest that the role 
    played by environment in shaping the structure of central galaxies may not be 
    that crucial in the \mhalo{} and \mstar{} ranges we discussed.}

    At the same time, the systematic differences we find, especially the more 
    extended stellar envelope of massive central galaxy in more massive halos, 
    seem to be consistent with the expectation of richer (minor) merging history
    in denser environment. 
    \update{
    Predicted by the ``two-phase'' scenario, the non-dissipative mergers, especially 
    the minor ones, should mainly deposit stellar mass in the outskirts, help 
    build the stellar halo while do not change the inner \mden{} profiles very 
    much (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).}

    We also explore the possible \mtot{} dependence of such difference.  
    Limited by the small sample we have, we can only afford to separate the 
    samples into two \mtot{} bins, and extend to slightly lower \mtot{} bound 
    ($11.5 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.7$ and 
     $11.7 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.9$).  
    After performing the same procedures of sample matching and comparison, 
    we show the results in Fig.\ref{fig:prof_2}.   
    Although the smaller sample leads to larger statistical uncertainties, 
    it is still interesting to see that the structural differences seem to 
    be more significant in the higher \mtot{} bin.  
    For the lower \mtot{} bin, the difference in the inner region becomes quite 
    uncertain, while there is still evidence of difference in the outskirt.  
    This result also has interesting implications in the assembly history
    of massive galaxies, and is worth more investigations with larger samples
    in the near future.

@@

\subsubsection{Environmental dependence of \mden{} profiles at fixed \minn{}}
    \label{sssec:sbp_minn}

    \update{Here, we compare the median \mden{} profiles of \rbcg{} and \nbcg{} galaxies
    after matching the two samples using \minn{} ($11.2 <$\logminn{}$ < 11.6$) and 
    redshift ($0.3 < z < 0.5$).
    We use the same matching procedure as in the previous section, and also put its 
    evaluation in Appendix.\ref{app:match}.
    As mentioned in the beginning, here we use \minn{} as the proxy of the 
    \mstar{} of the ``in-situ'' component. 
    We will discuss this assumption more in the Section~\ref{sec:discussion}, but 
    observations and simulations seem to support this claim in general. 
    In the previous section, we investigate the environmental dependence of structure 
    using ``total'' \mstar{}; here, we compare the massive galaxies in low- and 
    high-mass halos that share similar amount of ``in-situ'' component.}

    \update{
    As we can see in Fig.\ref{fig:prof_1} and the Appendix.\ref{app:D}, the \minn{} is 
    not affected by the physical size of PSF out to $z=0.5$.  
    For the 56 galaxies in this \rbcg{} sample, we achieve excellent matching 
    result using 375 \nbcg{} galaxies (see Fig.\ref{fig:match}; 
    median \logminn{}$\sim 11.35$).  
    Using the same method, we show their individual profiles, and the comparison of 
    their median \mden{} profiles on the right side of Fig.\ref{fig:prof_1}.}

    Unlike the \mtot{} matched samples, here we see very striking differences that 
    are already very significant even without any statistical test.     
    \update{
    It is easy to see that, when matched at the same \minn{}, the \mden{} profiles of 
    \rbcg{} and \nbcg{} galaxies are quite similar in the inner 5-10 kpc.
    However, outside inner 10-15 kpc, the \rbcg{} galaxies show much more prominent
    stellar envelope.}     
    Besides the differences in the median profiles, it is also worth discussing 
    the distributions of individual \mden{} profiles. 
    \update{
    Combining the \rbcg{} and \nbcg{} samples together, we should notice that 
    the slope of the \mden{} profile inside 10 kpc is quite uniform, and the dynamic 
    range of the \mden{} values is pretty small. 
    On the other hand, the outer \mden{} profiles of massive central galaxies 
    can have a larger range of slopes. 
    The ones from more massive halos on average have shallower outer \mden{} 
    profiles, which is in qualitative agreement with recent simulation results 
    (e.g. \citealt{Pillepich2014}).
    And, for both \rbcg{} and \nbcg{} samples, we find their outer profiles 
    clearly have much larger dynamic range of \mden{} values at fixed radius.
    This interesting diversity is also clearly illustrated by 
    Fig.\ref{fig:m100_m10_color}, where we show the 3-color images of randomly 
    selected massive central galaxies that have similar \minn{} 
    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
    but different \mtot{}.   
    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.}

    \update{
    Putting together, these results indicate that massive central galaxies with 
    similar \mstar{} in the ``in-situ'' components share very similar radial 
    \mstar{} distributions in the inner region. 
    Given the highly dissipative nature of the ``in-situ'' phase, this is consistent
    with the prediction that dissipative process like intense star-formation or 
    wet-merger should create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
    (e.g. \citealt{Hopkins2008}).
    On the other hand, the outer envelope of massive galaxies should be slowly 
    assembled through non-dissipative accretion process, where merger history 
    should play a essential role.  
    Therefore, it is reasonable to see that the central galaxy of more massive 
    halo has more significant stellar envelope than the one from lower mass 
    halo at fixed \mstar{} of their ``in-situ'' components.
    }
